\chapter{Data Reduction Software}

\section{Operational Phases}

The data reduction software will evolve through three phases in the life
of the PuMa-II instrument.

\begin{itemize}
\item {\bf offline} processing: performed after the recording has finished
\item {\bf simultaneous} processing: performed during the recording
\item {\bf diskless} processing: as above, but completely in memory
\end{itemize}

\subsection{Offline Data Reduction}

In the initial version of PuMa-II, the data reduction software will
operate only on data files stored on local disk space, and only after
the recording has completed.  After the observations have been
completed, the data files from each Primary node will be farmed out to
the Secondary nodes.  After each file has been copied, an entry will
be added to the log file that is monitored by the Configuration and
Scheduling software, which will attend to the data reduction as
described in Chapter 6.

\subsection{Simultaneous Data Reduction}

In the next stage of development, the data reduction software will be
run during the observation.  In this mode, data are sent directly to
Secondary nodes and written to disk.  As before, an entry will be made
in a log file and the Configuration and Scheduling software will
coordinate the data reduction.

\subsection{Diskless Data Reduction}

In the final stage of PuMa-II evolution, the data reduction software
will be able to keep up completely with the flow of data on the
Primary nodes.  In this case, the data is never written to disk, and
{\tt dspsr} will operate as a Read Client directly connected to the
Data Block.  Another Read Client may be written that will farm data
reduction tasks to a grid computing facility.  In this case, the data
reduction Read Client will have to incorporate the Configuration and
Scheduling tasks.

