\documentclass{scrreprt}
\usepackage{psfig}
\usepackage{atbeginend}

\makeatletter
\makeatother

\BeforeBegin{itemize}{\setlength{\topsep}{-2mm}}
\BeforeBegin{itemize}{\setlength{\partopsep}{-2mm}}

\BeforeBegin{enumerate}{\setlength{\topsep}{-2mm}}
\BeforeBegin{enumerate}{\setlength{\partopsep}{-2mm}}

\AfterBegin{itemize}{\setlength{\itemsep}{-1mm}}
\AfterBegin{enumerate}{\setlength{\itemsep}{-1mm}}

\begin{document}

\title{PuMa-II Software Specification}

\author{W.H.B.\ van Straten, B.W.\ Stappers, and K.\ Ramesh}

\maketitle
\tableofcontents{}

\begin{abstract}
This document specifies the software element of the 2nd generation of
the Dutch Pulsar Machine, PuMa-II, to be installed at the Westerbork
Synthesis Radio Telescope, WSRT, in 2005.  PuMa-II will consist of
eight data acquisition machines, called the \emph{Primary} nodes, and
a processing cluster of \emph{Secondary} nodes.

Each Primary Node will interface with one of the 20\, MHz, 12-bit
sampled outputs of the WSRT tied-array beam former.  On each machine,
a custom-designed interface card (PiC) will re-sample the data with
8-bit resolution and write the data to computer RAM via a direct
memory access (DMA) interface.  A large file storage facility,
implemented as internal RAID, will be used to store data locally, and
a high-speed interconnect will be used to send the data to Secondary
nodes for data reduction.

The communications plan and protocol used for sending the data from
Primary to Secondary node may change over the life of the PuMa-II
instrument.  Therefore, an adaptable and modular design philosophy has
been employed in the data flow control software, based on the use of a
ring buffer in shared memory.  This document contains an overview of
the software model, including a discussion of the design decisions
made at each level of command, control, and configuration.

\end{abstract}

\input{intro}
\input{data_flow}
\input{data_reduction}
\input{command_monitoring}
\input{pwc}
\input{control_interface}
\input{configuration_scheduling}
\input{summary}

\appendix
\input{ipc}
\input{header}
\input{log}
\input{socket}
\input{dada_pwc}
\input{dada_pwc_main}
\input{dada_prc_main}
\input{testing}

\end{document}
